%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {\href{https://www.iris-worldwide.com}{IRIS Worldwide}} % Organisation
    {London/New Delhi, India} % Location
    {Jul 2020 - Till Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the coordination of Samsung London projects, serving as the primary liaison with overseas teams, ensuring smooth communication and timely project completion.}
        \item {Spearheaded the conversion of the code base from Java to Kotlin and implemented an automated build and distribution system, optimizing the development workflow and reducing deployment time by 20\%.}
        \item {Dramatically improved crash analytics from 60\% to 98\%, resulting in a near escalation-free Android app experience. }
        \item {Currently in the process of uploading Samsung apps to the Google Play Store and managing the Firebase console. }
        \item {\textbf{Technical Skills:} Android(Java/Kotlin), Python(Web Scrapping), React Native, Ktor, Git(Bit-bucket, GitHub).}
      \end{cvitems}
    }
\vspace{0.5cm}
    \cventry
    {Project Manager/Developer} % Job title
    {\href{https://www.biocyteindia.com}{BioCyte India}} % Organisation
    {New Delhi, India} % Location
    {Aug 2018 - Jul 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided technical leadership for the Map My Health application, guiding a cross-platform team of 5 developers from inception to market launch.}
        \item {Established a clear data flow architecture for the app and website, ensuring data integrity and efficient operations.}
        \item {Collaborated with doctors and stakeholders to gather requirements and identify opportunities for app improvements, leading to a 15\% increase in user satisfaction.}
        \item {\textbf{Technical Skills:} Android(Java/Kotlin), Flutter, Git(Bit-bucket, GitHub).}
      \end{cvitems}
    }
\vspace{0.5cm}
    \cventry
    {Android Developer} % Job title
    {\href{https://ushyaku.com}{Ushyaku Software Solutions}} % Organisation
    {Gurugram, India} % Location
    {April 2017 - Jul 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with an overseas team to deliver app features and resolve critical issues, ensuring seamless project execution and on-time delivery.}
        \item {Implemented build automation to expedite build delivery to the overseas team, improving collaboration efficiency by 25\%}
        \item {Optimized layout and information hierarchy for enhanced user experience on large-screen devices, resulting in a 10\% increase in user engagement.}
        \item {\textbf{Technical Skills:} Android(Java), Git.}
      \end{cvitems}
    }
\vspace{0.5cm}
    \cventry
    {Software Engineer 1} % Job title
    {\href{https://www.linkedin.com/company/mobilyte/about/}{Mobilyte India Pvt Ltd}} % Organisation
    {Punjab, India} % Location
    {Jan 2015 - Mar 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Transitioned into an Android developer role, gaining expertise through active learning from senior developers.}
        \item {Received the first full-time offer from my internship batch in recognition of strong performance and rapid skill development.}
        \item {\textbf{Technical Skills:} Android(Java), Ubuntu Linux, Git.}
      \end{cvitems}
    }

\end{cventries}
