%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://www.iris-worldwide.com}{IRIS Worldwide}} % Organisation
    {\href{https://play.google.com/store/apps/details?id=com.samsung.uk.backstage}{Samsung Backstage}/\href{https://play.google.com/store/apps/details?id=com.samsung.uk.samsung.one}{One}/Roadshow} % Project
    {New Delhi, INDIA} % Location
    {Team Size: 1} % Team size(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed an app for Samsung store employees to access news, updates about Samsung launches, and earn points by completing tasks.}
        \item {Managed multiple app flavors using a single codebase.}
        \item {Coordinated with the overseas team and managed deliverables.}
        \item {Conducted daily analysis to optimize app performance and improve crash analytics, achieving a 95\% crash-free rate.}
        \item {\textbf{Technical Skills:} Android(Kotlin/Java), Firebase.}
        \item {\textbf{Soft Skills:} Technical Project Management, Time Management, Teamwork, Automated Pipelines, Documentation.}
      \end{cvitems}
    }
\vspace{0.5cm}
%---------------------------------------------------------
\cventry
  {\href{https://www.iris-worldwide.com}{IRIS Worldwide}} % Organisation
  {\href{https://play.google.com/store/apps/details?id=com.social_spectrum.mobile&hl=en_IN}{Social Spectrum}} % Project
  {Gurugram, INDIA} % Location
  {Team Size: 2} % Team Size(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {Built a cross-platform mobile application to support neurodiverse individuals and caregivers, with features like child profile management, event discovery, and community support.}
      \item {Implemented one-to-one and group chat using Firebase Realtime Database with push notifications for real-time communication.}
      \item {Developed caregiver tools including prescription/test record storage, event participation, and friend connections.}
      \item {Integrated Stripe payments and subscription management with support for free and premium tiers.}
      \item {Enhanced app reliability by reducing crashes and improving performance via Firebase Crashlytics and analytics-driven bug fixes.}
      \item {\textbf{Technical Skills:} React Native, Android (Kotlin), iOS (Swift), Firebase (Firestore, Realtime DB, Cloud Messaging), Stripe, Google Maps/Places API.}
      \item {\textbf{Soft Skills:} Project Management, Time Management, Team Collaboration, Automated Pipelines (CI/CD), Documentation.}
    \end{cvitems}
  }
  \vspace{0.5cm}
%---------------------------------------------------------
  \cventry
    {\href{https://www.iris-worldwide.com}{IRIS Worldwide}} % Organisation
    {\href{https://play.google.com/store/apps/details?id=com.beejameditation.beeja}{Beeja Meditation}} % Project
    {New Delhi, INDIA} % Location
    {Team Size: 3} % Team Size(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a mobile application for user meditation with minimal user interaction.}
        \item {Coordinated with the client, shared details with the team, and managed deliverables.}
        \item {Improved crash analytics by 10\% by identifying and rectifying key error-prone areas.}
        \item {\textbf{Technical Skills:} Android(Kotlin), Firebase, Aflorithmic.}
        \item {\textbf{Soft Skills:} Project, Time and Team Management, Teamwork, Automated Pipelines, Documentation.}
      \end{cvitems}
    }

  %---------------------------------------------------------
\end{cventries}
\vspace{0.5cm}
%---------------------------------------------------------
   \cventry
    {\href{https://www.biocyteindia.com}{BioCyte India}} % Organisation
    {\href{https://play.google.com/store/apps/details?id=gov.ncpcr.masi}{MASI Inspection App By NCPCR }} % Project
    {New Delhi, INDIA} % Location
    {Team Size: 1} % Team Size(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a Government of INDIA initiative to monitor inspections of organizations and shelter homes, ensuring compliance with government guidelines.}
        \item {Implemented robust error handling, reducing crashes by 15\%.}
        \item {\textbf{Technical Skills:} Android(Kotlin), Firebase, Bit-bucket Pipeline.}
        \item {\textbf{Soft Skills:} Project, Time and Team Management, Teamwork, Automated Pipelines, Documentation.}
      \end{cvitems}
    }
%---------------------------------------------------------
